Determinism, Complexity, and Predictability in Computer Performance

### 2014-03-10 intro.tex
A bit more wordsmithing on intro.tex

\section{Introduction  }\label{sec:intro}
{\color{blue}[[EDITABLE]]}
%****NOTES START HERE****

@@

Complicated time-series data are ubiquitous in modern scientific
research.  The complexity of these data spans a wide range.  On the
low end of this spectrum are time series that exhibit perfect
predictive structure, i.e, signals whose future values can be
successfully predicted from past values.  In situations like this,
there is an underlying process that generates information and/or
transmits it from the past to the future in a perfectly predictable
fashion.  Constant or periodic signals, for example, fall in this
class.  On the opposite end of this spectrum are signals that are what
we call \emph{fully complex}, where the underlying generating process
transmits no information at all from the past to the future.  White
noise and random-walk processes fall in this class.  In fully complex
signals, knowledge of the past gives no insight into the future,
\emph{regardless} of what model one chooses to use.  Signals in the
midrange of this spectrum---e.g., deterministic chaos---pose
interesting challenges from a modeling perspective.  In these signals,
enough information is being transmitted from the past to the future
that an \emph{ideal} model---one that captures the generating
process---can forecast the future behavior of the observed system with
high accuracy.

@@

[[Following is a good start at an abstract. It doesn't need to be
    reiterated in the introduction.]]  This paper provides insight
into when, why, and how forecast strategies fail when they are applied
to complicated time series by empirically estimating their inherent
complexity. [[Liz, do you think here would be better for the sentence
    about we are not the first, or is above where I asked Ryan to
    insert it ok? I worry it would muddy the water of this synopsis
    paragraph.]] We focus here on the specific example of computer
performance but believe the results apply to a much broader class of
time series. We conjecture that the complexity of traces from these
systems---which results from the inherent dimension, non-linearity,
and non-stationarity, as well as from measurement issues like noise,
aggregation, and finite data length---is \emph{empirically
  quantifiable}.  To validate this conjecture we model 120 different
performance traces using a variety of forecasting models.  We then
compare the empirically estimated \emph{complexity} with the accuracy
of each forecast method.

>>>>

\section{Introduction  }\label{sec:intro}
%****NOTES START HERE****

@@

Complicated time-series data are ubiquitous in modern scientific
research.  The complexity of these data spans a wide range.  On the
low end of this spectrum are time series that exhibit perfect
predictive structure, i.e, signals whose future values can be
successfully predicted from past values.  This can be viewed as the
output of an underlying process that generates information and/or
transmits it from the past to the future in a perfectly predictable
fashion.  Constant or periodic signals, for example, fall in this
class.  On the opposite end of this spectrum are signals that are what
we call \emph{fully complex}, where the underlying generating process
transmits no information at all from the past to the future.  White
noise and random-walk processes fall in this class.  In fully complex
signals, knowledge of the past gives no insight into the future,
\emph{regardless} of what model one chooses to use.  Signals in the
midrange of this spectrum---e.g., deterministic chaos---pose
interesting challenges from a modeling perspective.  In these signals,
enough information is being transmitted from the past to the future
that an \emph{ideal} model---one that captures the generating
process---can forecast the future behavior of the observed system with
high accuracy.

@@
